Improved Bounds for Online Balanced Repartitioning

### 2020-04-29 paper/disc20clustering.tex
Title suggestion
backup k=2 draft

@@

An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
or \emph{remotely} at cost~1
if they are located in different clusters.
We refer to these two types of requests as \emph{internal}
and \emph{external} requests, respectively.
Before serving a request,
an online algorithm may perform a \emph{repartition},
%(i.e., \emph{reconfigure}).
i.e.,
it may move (``migrate'') some nodes into clusters different from their current clusters, while respecting the capacity of every cluster. 
Afterwards, 
the algorithm serves the  request.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $\ALG$,
its cost,
denoted by $\ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $\ALG$ while serving the sequence $\sigma$.

@@

Algorithm Alg:
maintain a counter $C_{\set{u,v}}$ for each pair of nodes $\set{u,v}$ and increment it on every remote request between $u$ and $v$.
Once $C_{\set{u,v}} = \lambda:=2\alpha$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $u$ or $v$ resides.

\begin{theorem} \label{thm:k=2}
	The algorithm is (strictly) 4-competitive.
\end{theorem}

We charge both OPT and Alg whenever Alg collocates a pair (i.e., on a collocation event).
%More precisely,we charge them only the cost of the collocation, per such event.
%Hence,we charge the cost of  this collocation to OPT for the first time.
Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
which  costs $2\alpha$.
%We charge OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
paying the price of only one migration per pair.
This observation suggests that we can't charge OPT more than $\alpha$ per collocation,
even when OPT actually pays more that that.
E.g.,
OPT can collocate two costly pairs with a single swap if
it has both pairs on the cut of  the same two clusters.
Later, Alg collocates those pairs with two swaps (see Figure \ref{fig:TBD}).
Hence,
whenever OPT collocates a pair,
we charge OPT only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ for Alg).

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	\mahmoud{still proof sketch}
	Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$
	immediately after arrival of the $t$th request,
	$\sigma_t$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t \geq 1$,
	Alg collocates the pair,
	which means $ C^t_{\set{u,v}} = \lambda$ immediately before Alg resets the counter.
	Let $\sigma_{t''}, t''<t$ be the last request (before $\sigma_{t}$)
	upon which Alg collocates $\set{u,v}$.
	Let $t'$ s.t.~$t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some other pair that shares a node with $\set{u,v}$,
	denoted by $\set{u,v'}, v' \neq v$.
	In case the first collocation of $\set{u,v}$ occurs at $t$,
	if the pair is collocated in the initial configuration then
	we set $t''=0$,
	else,
	we set $ t'' = -\infty, t'=0$.
	%e.g., the request $\sigma_{t'} = \set{u,v'}$.
	%By Alg's definition,
	%$C^{t'}_{\set{u,v'}}  = C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to $\set{u,v}$
	between times $t'$ and $t$ by $\sigma_{\set{u,v}}[t',t]$.
	Thus,
	$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
	The overall cost of requests that increase the counter,
	i.e.~requests in $\sigma_{\set{u,v}}[t',t]$,
	and the moving cost,
	incurred by Alg is $\lambda + 2\alpha$.
  %That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.

	We distinguish three cases for the cost incurred by OPT due to $\set{u,v}$.

  \begin{enumerate}
  \item Case i)
	OPT has $\set{u,v}$ separated (in OPT's configuration) during $[t',t]$
	and therefore it pays $\lambda$.
	We charge OPT $\lambda/2 = \alpha$.
%	The remaining cost will be used in a latter case.

  \item Case ii)  
	OPT collocates $\set{u,v}$ some time during $[t',t]$.
	Any cost that we charge to OPT upon $\sigma_{t''}$,
	accounts for OPT's actions before $t''$.
	Therefore in this case,
	we charge OPT the (unaccounted) cost $\alpha$.

  \item Case iii)
	$t'' \geq 0$ and OPT has $\set{u,v}$ collocated before $t''$ and keeps them collocated during $[t'',t]$.
	In this case OPT doesn't pays any cost for requests in $\sigma_{\set{u,v}}[t'',t]$ and
	we can't charge it directly.
	However,
	OPT must pay $\lambda$ for all requests in $\sigma_{\set{u,v'}}[t'',t']$,
	 i.e.,
	 Case (i) applies to $\set{u,v'}$  at $t'$ and
 	we charge only $\lambda/2$ to OPT (at $t'$).
	This means,
	we can charge OPT an additional $\alpha$,
	i.e.~the remaining cost of requests $\sigma_{\set{u,v'}}[t'',t']$.
%	Intuitively, at $t$,  we charge $\alpha$ to OPT for separating $\set{u,v}$ (at $t'$) by Alg.
  \end{enumerate}

@@

	It remains to charge both Alg and OPT for requests that do not lead to collocations when the sequence ends.
	Consider  pairs $\set{u,v}$ and $\set{u,v'}$ and
	times $t'' < t' < t = t_m$ as defined previously.
	Assume $\sigma_{\set{u,v}}[t'', t_m] \leq \lambda - 1$.
	This means Alg has the pair separated at $t_m$
	and paid the (communication) cost $r_{\set{u,v}} := | \sigma_{\set{u,v}}[t'', t_m]|$.
	If OPT has the pair separated during $[t'',t_m]$ then it pays $r_{\set{u,v}}$.
	If OPT collocates the pair some time during $[t'', t]$ then analogous to Case (ii),
	we charge it $\alpha$.
	Otherwise,
	if OPT collocates the pair before $t''$,
	then we charge it $\alpha$ analogously to Case (iii).
	Hence, 
	$Cost(OPT)_{\set{u,v}} / Cost(Alg)_{\set{u,v}} =
	\max \set{ r_{\set{u,v}}/ \alpha \leq (\lambda-1) / \alpha , (\lambda + 2\alpha)/ \alpha} = 4$.
%	The claim follows from here.
\end{proof}

@@

>>>>

\maciek{Title discussion: "Online Balanced Graph Partitioning: Understanding the role of clusters". Reason: all our results most notably pertain to the number of clusters.}

@@

An algorithm serves a communication request between two nodes
either \emph{locally} at cost~0
if they are collocated,
or \emph{remotely} at cost~1
if they are located in different clusters.
We refer to these two types of requests as \emph{internal}
and \emph{external} requests, respectively.
\mahmoud{"Before serving a request": does this mean that only after a request arrives and before serving it we migrate? In our algorithms we migrate after serving $\lambda$ requests. Do we have discrepancy with the model?}
Before serving a request,
an online algorithm may perform a \emph{repartition},
%(i.e., \emph{reconfigure}).
i.e.,
it may move (``migrate'') some nodes into clusters different from their current clusters, while respecting the capacity of every cluster. 
Afterwards, 
the algorithm serves the  request.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $\ALG$,
its cost,
denoted by $\ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $\ALG$ while serving the sequence $\sigma$.

@@

Algorithm Alg:
maintain a counter $C_{\set{u,v}}$ for each pair of nodes $\set{u,v}$ and increment it on every remote request between $u$ and $v$.
Once $C_{\set{u,v}} = \lambda$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $u$ or $v$ resides.

\begin{theorem} \label{thm:k=2}
	The algorithm is (strictly) 6-competitive.
\end{theorem}

We charge both OPT and Alg whenever Alg collocates a pair (i.e., on a collocation event).
%More precisely,we charge them only the cost of the collocation, per such event.
%Hence,we charge the cost of  this collocation to OPT for the first time.
Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
which  costs $2\alpha$.
%We charge OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
paying the price of only one migration per pair.
This observation suggests that we can't charge OPT more than $\alpha$ per collocation,
even when OPT actually pays more than that.
E.g.,
OPT can collocate two costly pairs with a single swap if
it has both pairs on the cut of  the same two clusters  (see Figure \ref{fig:TBD}).
Later, Alg collocates those pairs with two swaps.
Hence,
whenever OPT collocates a pair,
we charge OPT only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on Alg).

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before Alg resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
%	In case the first collocation of $\set{u,v}$ occurs at $t$,
%	if the pair is collocated in the initial configuration then
%	we set $t''=0$,
%	else,
%	we set $ t'' = -\infty, t'=0$.
	We denote the set of all requests to $\set{x,y}$
	during $(t_1,t_2]$ by $\sigma_{\set{x,y}}(t_1,t_2]$.
	If $t$ is the first time Alg collocates $\{u,v\}$ then we can charge
	OPT $\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	 or $\alpha$ for collocating the pair and serving them with no additional cost.
	Therefore in this case ,
	OPT pays $\min{\{ \lambda,\alpha \}}$.
	Else,
	let $t'$, $t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some (intersecting) pair
	$\{x,y\} \neq \{u,v\}, x \in \{u,v\}$, 
	e.g.,
	$\{x,y\}=\{u,v'\}$.
%	I.e., $ C^{t'}_{\set{u,v'}} = \lambda$.
	Similarly,
	if $t'$ is not the first time that Alg has $\{u,v'\}$ collocated
	then let $t''<t'$ be the last time before $t'$ when Alg separates $\set{u,v'}$.
	Else,
	$\{u,v'\}$ is not collocated in the initial configuration and let $t''=0$.
	Then by these definitions,
	we have
	$| \sigma_{\set{u,v'}}(t'',t'] | = | \sigma_{\set{u,v}}(t',t] |  =  \lambda$.
	The overall cost of requests in $\sigma_{\set{u,v}}(t',t]$,
	and the moving cost,
	incurred by Alg is
	$\lambda + 2\alpha$.
	We charge OPT the cost of serving requests in
	$\sigma_{\{u,v'\}}[t'',t']$ ($\sigma_{\{u,v\}}(t',t]$ ) 
	that it pays only within the interval $(t'', t']$ ($(t', t]$).
	Observe that for requests in $r_t := \sigma_{\{u,v'\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t]$,
	OPT must pay at least
	$\min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$
	within $(0,m]$,
	regardless of its choices.
	Based on this observation,
	we distinguish three cases of OPT's choices
	while it serves requests in	$r_t $.
	We denote its cost by
	$\mathit{Cost}_{\mathit{OPT}} (r_t) := \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v'\}}(t'',t']) 
	+ \mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}(t',t]) $.
	\begin{enumerate}[label=\roman*.]
		\item
		OPT collocates $\{u,v'\}$ and $\{u,v\}$  at times  $t''$ and $t'$ respectively
		and keeps them so during $(t'',t']$ and $(t',t]$, respectively.
		Therefore it serves all requests in $r_t$ with no additional cost and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = 2\alpha$.
		\item
		OPT has $\{u,v\}$ ($\{u,v'\}$) already collocated at $t'$ ($t''$) as well as during $(t',t]$ ($(t'',t]$),
		and has $\{u,v'\}$ ($\{u,v\}$) separated during $(t'',t']$ ($(t',t]$).
		Hence,
		it pays only $\lambda$ for serving all requests in $r_t$ and
		$\mathit{Cost}_{\mathit{OPT}} (r_t) = \lambda$
		\item
		OPT has $\{u,v'\}$ ($\{u,v\}$) already  collocated at $t''$ ($t'$)  and also during $(t'',t']$ ($(t', t])$,
		 and it collocates $\{u,v\}$ ($\{u,v'\}$) at $t'+1$ ($t''+1$) paying $\alpha$.
%		Therefore it pays only $\alpha$ during $[t'',t]$,
%		for collocating $\{u,v'\}$
%	    and for the one request to $\{u,v\}$ at $t'$.
%		I.e., it pays zero for every other  request in $r_t$.
Then,
$\mathit{Cost}_{\mathit{OPT}} (r_t) = \alpha$.
	\end{enumerate}
	 In every of these cases,
   	we have
   	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.
  	OPT may deviate from these cases,
	e.g.~by collocating a pair after partially paying for requests to this pair.
	 However,
	 any deviation only increases the cost to OPT.
	 \mahmoud{It would be better to describe and bound the "deviation" formally.}
	Therefore in any case,
 	$\mathit{Cost}_{\mathit{OPT}} (r_t) \geq  \min{ \{ \lambda, \alpha \}}$.

	It remains to charge both Alg and OPT for requests that do not lead to collocations until the  end of the sequence at $m$.
	Assume $\{u,v\}$ is not collocated at $m$
	and $0 < C^{m}_{ \{u,v\} } < \lambda $,
	which means Alg pays $C^{m}_{ \{u,v\} }$
	for requests to $\{u,v\}$ not accounted previously.
	If $\{u,v\}$ is not collocated in the initial configuration
	and Alg never collocates it through the sequence,
	then $ C^{m}_{ \{u,v\} } =| \sigma_{\{u,v\}}[0,m] |$.
	We charge OPT the cost
	$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[0,t]) 
	\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
	for collocating this pair or (and) paying (partially) for requests in $\sigma_{\{u,v\}}[0,t]$.
	Else,
	either $\{u,v\}$ is collocated in the initial configuration
	or Alg collocates it at some point.
	Then there exists an intersecting pair $\set{u,v'}$
	that is collocated by Alg at $t' < m$ (separating $\{u,v\}$).
	We define times $t'' < t' < m$ similarly to the case where Alg collocates $\{u,v\}$.
	Let $r_{\{u,v\}} := \sigma_{\{u,v'\}} (t'',t'] \cup \sigma_{\{u,v\}} (t',t]$.
	Then,
	we apply cases (i) to (iii) for $t=m$ in an analogous way,
	after replacing $\lambda$ with $C^{m}_{ \{u,v\}}$.
	Thus, 
	we obtain
	 $\mathit{Cost}_{\mathit{OPT}} (r_{\{u,v\}}) 
	 \geq  \min{ \{ C^{m}_{ \{u,v\}}, \alpha \}}$.

	 Next, we sum up all costs charged to OPT.
	 Observe that by definition,
	 $r_{t'} \cap r_t = \sigma_{\{u,v'\}}[t'',t']$.
	 This means,
	 the cost of r.h.s.~to OPT is counted at most two times in the expression
	 $\mathit{Cost}_{\mathit{OPT}} (r_{t'}) + \mathit{Cost}_{\mathit{OPT}} (r_t)$.
	 Hence,
	 for all collocations performed by Alg and for $t=m$,
	 OPT pays at least 
	 $\sum_{ 0 < t \leq |\sigma|} \mathit{Cost}_{\mathit{OPT}} (r_t) / 2$.
	Let
	$T := \{ 0 < t \leq m ~\vert~ \exists \{u,v\}: C^{t}_{\{u,v\}} = \lambda \}$.
	By setting $\lambda= \alpha$
	we obtain
\begin{align*}
	\mathit{Cost}_{\mathit{ALG}} (\sigma)	/
	 \mathit{Cost}_{\mathit{OPT}} (\sigma)
	 &=
	 \Big(
	 \sum_{ t \in T}(\lambda + 2\alpha) +
	 \sum_{\{u,v\}} C^{m}_{\{u,v\}}
	 \Big)	 \big /
	 \Big(
	 \sum_{ t \in T} \mathit{Cost}_{\mathit{OPT}} (r_t) / 2
	 + \sum_{\{u,v\}}\mathit{Cost}_{\mathit{OPT}} (r_{\{u,v\}})  / 2 
	 \Big)	\\
	 &\leq
	 \Big(
	 \sum_{ t \in T}(\lambda + 2\alpha) +
	 \sum_{\{u,v\}} C^{m}_{\{u,v\}}
	 \Big)	 \big /
	 \Big(
	 \sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  / 2
	 + \sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \}  / 2 } 
	 \Big)	\\
	 &=
	 \Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  / 2
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  / 2 
	\Big)	\leq 6
\end{align*}.
	%	The claim follows from here.
\end{proof}

\begin{comment}
We charge both OPT and Alg whenever Alg collocates a pair (i.e., on a collocation event).
%More precisely,we charge them only the cost of the collocation, per such event.
%Hence,we charge the cost of  this collocation to OPT for the first time.
Alg collocates a pair always with a swap (i.e., two simultaneous migrations),
which  costs $2\alpha$.
%We charge OPT only for requests up to the one that triggers a collocation (i.e., not for later requests on the same pair).
OPT may save some costs by collocating multiple pairs at once (before they incur too much cost),
paying the price of only one migration per pair.
This observation suggests that we can't charge OPT more than $\alpha$ per collocation,
even when OPT actually pays more than that.
E.g.,
OPT can collocate two costly pairs with a single swap if
it has both pairs on the cut of  the same two clusters.
Later, Alg collocates those pairs with two swaps (see Figure \ref{fig:TBD}).
Hence,
whenever OPT collocates a pair,
we charge OPT only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ for Alg).

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	\mahmoud{not correct}
%	Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$
%	immediately after arrival of the $t$th request,
%	$\sigma_t$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t \geq 1$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	immediately before Alg resets the counter is $\lambda$.
	That is, $ C^t_{\set{u,v}} = \lambda$.
	Let $\sigma_{t''}, t''<t$ be the last request (before $\sigma_{t}$)
	upon which Alg collocates $\set{u,v}$.
	Let $t'$, $t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some other pair that shares a node with $\set{u,v}$,
	 e.g.~$\set{u,v'}, v' \neq v$.
	In case the first collocation of $\set{u,v}$ occurs at $t$,
	if the pair is collocated in the initial configuration then
	we set $t''=0$,
	else,
	we set $ t'' = -\infty, t'=0$.
	We denote the set of all requests to $\set{u,v}$
	during $[t_1,t_2]$ by $\sigma_{\set{u,v}}[t_1,t_2]$.
	Thus,
	$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
	The overall cost of requests that increase the counters of intersecting pairs,
%	i.e.~requests in $\sigma_{\set{u,v}}[t'',t]$,
	and the moving cost,
	incurred by Alg is
	$\lambda + 2\alpha$.
  %That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.

	We distinguish three cases for the cost incurred by OPT with respect to the collocation of $\set{u,v}$ at $t$.

  \begin{enumerate}
  \item Case i)
	OPT has $\set{u,v}$ separated (in OPT's configuration) during $[t',t]$
	and therefore it pays $\lambda$.
	We charge OPT $\lambda/2$, i.e.,
	$\mathit{Cost}^{t}_{\{u,v\}} (\mathit{OPT})= \lambda / 2$.

  \item Case ii)  
	OPT collocates $\set{u,v}$ some time during $[t'',t]$ and pays $\alpha$.
	We charge it $\alpha/2$, i.e.,
	$\mathit{Cost}^{t}_{\{u,v\}} (\mathit{OPT}) = \alpha / 2$.

  \item Case iii)
	$t'' \geq 0$ and OPT has $\set{u,v}$ already collocated before $t''$.
%	 and keeps them collocated during $[t'',t]$.
	In this case,
	OPT possibly pays zero for requests in $\sigma_{\set{u,v}}[t'',t]$.
	However,
	by assumption,
	 Alg collocates $\{u,v'\}$ at $t'$ and
	OPT doesn't have $\{u,v'\}$ collocated through the entire
	$[\tau^{t''}_{\{u,v'\}}, t']$.
	This implies that only cases (i) or (ii) applies to $\{u,v'\}$ at $t'$.
	That is,
	OPT pays $\min \{ \lambda, \alpha \}$,
	and it is charged $\min \{ \lambda/2, \alpha/2 \}$
	w.r.t.~the collocation of $\{u, v'\}$ at $t'$.
	Hence,
	we can charge it  $\min \{ \lambda/2, \alpha/2 \}$ in addition to the  cost already charged.
%	i.e.~the remaining (unaccounted) cost of requests in $\sigma_{\set{u,v'}}[t'',t']$.
%	Intuitively, at $t$,  we charge $\alpha$ to OPT for separating $\set{u,v}$ (at $t'$) by Alg.
  \end{enumerate}

@@

	It remains to charge both Alg and OPT for requests that do not lead to collocations when the sequence ends.
	Consider  pairs $\set{u,v}$ and $\set{u,v'}$ and
	times $t'' < t' < t = t_m$ as defined previously.
	Assume $\sigma_{\set{u,v}}[t'', t_m] \leq \lambda - 1$.
	This means Alg has the pair separated at $t_m$
	and paid the (communication) cost $r_{\set{u,v}} := | \sigma_{\set{u,v}}[t'', t_m]|$.
	If OPT has the pair separated during $[t'',t_m]$ then it pays $r_{\set{u,v}}$.
	If OPT collocates the pair some time during $[t'', t]$ then analogous to Case (ii),
	we charge it $\alpha$.
	Otherwise,
	if OPT collocates the pair before $t''$,
	then we charge it $\alpha$ analogously to Case (iii).
	Hence, 
	$Cost(OPT)_{\set{u,v}} / Cost(Alg)_{\set{u,v}} =
	\max \set{ r_{\set{u,v}}/ \alpha \leq (\lambda-1) / \alpha , (\lambda + 2\alpha)/ \alpha} = 4$.
%	The claim follows from here.
\end{proof}
\end{comment}

@@

\maciek{$\sigma_t$ undefined (I know what it is, though). \mahmoud{added inline def. Do we have a global def for this?}}
\maciek{Define $C^t$ to use once \mahmoud{already defined! I don't get it.}}
\maciek{A word "Obviously" is unnecessary, and most people, including me are allergic to it in writing
\mahmoud{obviously that's true! connect the two sentences}}
